Enzo+Moray: Radiation Hydrodynamics Adaptive Mesh Refinement Simulations with Adaptive Ray Tracing

### 2010-09-08 ms.tex
Offset error bars in strong scaling figure.  Added a few sentences to the section.

\begin{figure}[t]
  \epsscale{0.8}
  \plotone{fig/strong_v1.eps}
  \caption{\label{fig:strong} Strong scaling test with a $256^3$ AMR
    calculation of cosmological reionization.  The error bars
    represent the minimum and maximum time spent on a single core and
    measures load balancing.  The hydrodynamics and non-equilibrium
    chemistry solvers scale well.  Unfortunately the communication of
    rays does not scale in this problem, where as the ray tracing
    scales relatively well.}
  \epsscale{1}
\end{figure}

Strong scaling tests shows how the problem scales with the number of
processors for the same problem.  The overhead associated with the
structured AMR framework in \enzo~can limit the strong scalability.
One key property of strong scaling is that each processor must have
sufficient work to compute, compared to the communication involved.
Here we use a small-box reionization calculation with $L_{\rm box} =
3$ Mpc/h, a resolution of $256^3$, and six levels of refinement.  We
measure the time spent on the hydrodynamics, non-equilibrium
chemistry, ray tracing, and radiation transport communication in a
timestep lasting 1 Myr, at $z=10$.  There are nine radiative transfer
timesteps in this period.  The box has 675 point sources, ??? AMR
grids, and ??? computational cells in this calculation at this
redshift.  In the first radiative transfer timestep, ??? and ??? ray
segments are traced with and without ray merging.  The ionized volume
fraction is ???.  The calculations are performed on the Nehalam nodes
on Pleiades on 2$^n$ cores, where $n = [2,...,8]$.

>>>>

\begin{figure}[t]
  \epsscale{0.8}
  \plotone{fig/strong_v1.eps}
  \caption{\label{fig:strong} Strong scaling test with a $256^3$ AMR
    calculation of cosmological reionization.  The error bars
    represent the minimum and maximum time spent on a single core and
    measures load balancing.  Each point has been slightly offset to
    make the error bars distinguishable.  The hydrodynamics and
    non-equilibrium chemistry solvers scale well.  Unfortunately the
    communication of rays does not scale in this problem, where as the
    ray tracing scales relatively well.}
  \epsscale{1}
\end{figure}

Strong scaling tests shows how the problem scales with the number of
processors for the same problem.  The overhead associated with the
structured AMR framework in \enzo~can limit the strong scalability.
One key property of strong scaling is that each processor must have
sufficient work to compute, compared to the communication involved.
In our experience, non-AMR calculations exhibit much better strong
scaling than AMR ones because of reduced inter-processor
communication.  We use an AMR simulation to demonstrate the scability
of Enzo+Moray in a demanding, real-world calculation.  Here we use a
small-box reionization calculation with $L_{\rm box} = 3$ Mpc/h, a
resolution of $256^3$, and six levels of refinement.  We measure the
time spent on the hydrodynamics, non-equilibrium chemistry, ray
tracing, and radiation transport communication in a timestep lasting 1
Myr, at $z=10$.  There are nine radiative transfer timesteps in this
period.  The box has 675 point sources, ??? AMR grids, and ???
computational cells in this calculation at this redshift.  In the
first radiative transfer timestep, ??? and ??? ray segments are traced
with and without ray merging.  The ionized volume fraction is ???.
The calculations are performed on the Nehalam nodes on Pleiades on
2$^n$ cores, where $n = [2,...,8]$.
